\\textsc{Mathematical Description}

### 2023-03-13 100-math-description/GR-sslcm-math-description.Rmd
Use power function in DD growth math doc
Update math doc to account for 50:50 sex ratio
See #167, should have included this in #171

\begin{equation}
E_{y,j} = \sum_o^{n_o} \sum_k^{n_k} S^{a}_{y,k,o,j} \cdot \Omega_{k,j} \cdot f_{k}
(\#eq:get-E)
\end{equation}

We calculated the proportion of spawners at age that are female ($\Omega_{k,j}$) from carcass survey data and averaged across years and fecundity ($f_k$) from samples taken from Grande Ronde-origin hatchery broodstock.
We supplied both quantities to the model assuming no error or inter-annual variability.

@@

In addition to density-dependent egg-to-parr survival (eq. \@ref(eq:get-phi-E-Pb-dot)), we also wished to model the size of parr at the end of summer as a function of density.
It is well known that juvenile survival is related to body size \todo{Insert references about survival being related to size} and if parr size is density-dependent, that would provide the possibility of modeling variability in survival later in life (overwinter rearing and migration out-of-basin) based on a density-dependent process that occurred earlier.
We modeled expected parr mean length ($\dot{L}^{P^{b}}_{y,j}$, mm fork length) as a log-linear function of egg density:

\begin{equation}
\log\left(\dot{L}^{P^{b}}_{y,j}\right) = \omega_{0,j} + \omega_{1,j} \cdot \frac{E_{y,j}}{\mathrm{WUL}_j}
(\#eq:get-L-Pb-dot)
\end{equation}

>>>>

\begin{equation}
E_{y,j} = \sum_o^{n_o} \sum_k^{n_k} S^{a}_{y,k,o,j} \cdot \Omega_{k} \cdot f_{k}
(\#eq:get-E)
\end{equation}

We assumed that spawners age-4 or age-5 were 50% female and age-3 spawners were all male (i.e., $\Omega_{k=1} = 0;\;\Omega_{k \in [2,3]} = 0.5$; approximately equal to values estimated from carcass data) and estimated fecundity ($f_k$) from samples taken from Grande Ronde-origin hatchery broodstock.
We supplied both quantities to the model assuming no error or inter-annual variability.

@@

In addition to density-dependent egg-to-parr survival (eq. \@ref(eq:get-phi-E-Pb-dot)), we also wished to model the size of parr at the end of summer as a function of density.
It is well known that juvenile survival is related to body size \todo{Insert references about survival being related to size} and if parr size is density-dependent, that would provide the possibility of modeling variability in survival later in life (overwinter rearing and migration out-of-basin) based on a density-dependent process that occurred earlier.
We modeled expected parr mean length ($\dot{L}^{P^{b}}_{y,j}$, mm fork length) as a power function of egg density, which expressed on the logarithmic scale was:

\begin{equation}
\log\left(\dot{L}^{P^{b}}_{y,j}\right) = \omega_{0,j} + \omega_{1,j} \cdot \log\left(\frac{E_{y,j}}{\mathrm{WUL}_j}\right)
(\#eq:get-L-Pb-dot)
\end{equation}
